# Data

-   Sources
-   Description
-   Wrangling/cleaning
-   Spotting mistakes and missing data (could be part of EDA too)
-   Listing anomalies and outliers (could be part of EDA too)

setting eval=FALSE will not run the code when knitting the document


## check the CSV

```{r load_data, cache=TRUE, eval=FALSE}
#load csv with here
df <- read.csv(here("data/reddit_comments_15k.csv"))
(head(df, 10))
summary(df)
```

## Clean the data

```{r clean_data, cache=TRUE, eval=FALSE, echo=TRUE}
#show column that contains 'deleted'
df[df$body == '[deleted]',]

#remove rows where 'deleted' in body or author
df <- df[!(df$body == '[deleted]' | df$author == '[deleted]'),]

# Remove any series of 'x' characters from the 'body' column
df$body <- gsub("xx+", "", df$body)
df$body <- gsub("XX+", "", df$body)

#show number of rows
nrow(df)

#remove 3 first character of the col parent_id and create a new column
df$parent_id_small <- substr(df$parent_id, 4, nchar(df$parent_id))

#remove weblink
df$body <- gsub("http\\S+", "", df$body)

#remove all quotes or special characters in text fields.
df$body <- gsub("[^[:alnum:][:space:]]", "", df$body)

#show random sample of df
set.seed(123)
df[sample(nrow(df), 1000),]
summary(df)

#save csv as cleaned (a reecrire qd on clean +)
#write.csv(df, here("data/15k_cleaned.csv"), row.names = TRUE)

#create new dataset as csv but without col body
#write.csv(df[, -9], here("data/15k_cleaned_no_body.csv"), row.names = TRUE)
```

For rendering reasons, we load the cleaned dataset.
Here is a sample of 20 observations from the dataset. We decided to show only the columns 'author' and 'body' for the sake of simplicity.

### Load cleaned data

```{r load cleaned data, eval=TRUE, echo=TRUE}
df <- read.csv(here("data/15k_cleaned.csv"))

#show comment with 0 words
df[df$body == "",]
#remove them
df <- df[df$body != "",]

df.no_body <- read.csv(here("data/15k_cleaned_no_body.csv"))

#show only columns 'author' and 'body' with reactable
reactable(
  head(df[, c("author", "body")], 20),
  searchable = TRUE,
  defaultPageSize = 10,
  sortable = TRUE,
  resizable = TRUE,
  highlight = TRUE,
  paginationType = "numbers")
```

